---
title: "Analysis of day 1 session (contingency learning) on PREMUP-priors."
output: html_document
---

Author: Javier Ortiz-Tudela (Goethe Uni)
Started on: 27.01.20
Last updated on: 05.06.20

```{r setup, include=FALSE}
## Load libraries.
library(ggpubr)
library(rstatix)
library(psycho)
library(gridExtra)
library(dplyr)

## Set directories
if(Sys.info()["sysname"]=="Linux"){
  data_dir <- "/home/javier/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
  out_dir <- "/home/javier/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
}else{
  data_dir <- "/Users/javierortiz/Documents/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
  out_dir <- "/Users/javierortiz/Documents/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
}

## Read-in the data
full_name <- paste(data_dir, "group_task-learning.csv", sep="")

# Since the data is in a CSV file, you can read it with the csvread function.
temp <- read.csv2(full_name, sep=";")

# The data file contains a lot of information that we will not need now.
data <- subset(x = temp,
               select = c("participant", "iteration_index", "trial_index", "trial_acc", "scn_condition", "scn_cat", "PE_level"))

```

## Compute overall performance
I will compute mean accuracy by prior strength in of Day1. I will use this information to discard participants below. 

```{r}
# Aggregate
agg_data <- data %>% 
  group_by(participant) %>% 
  summarise(mean_acc = mean(trial_acc),
            sd_acc = sd(trial_acc))
# Plot
ggplot(data = agg_data,
       mapping = aes(x=1, y = mean_acc)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1)) +
  labs(title = paste("Overall prediction acc"))
```

A rather arbitrary threshold of .4 to include _bad luck_ participants which migh have encountered a long train of mismatch trials. I should probably re-consider this.

```{r}
# Poor performers
poor_performers <- agg_data$participant[agg_data$mean_acc < .7]

# Remove poor performers
data <- data %>% 
  filter(!(participant %in% poor_performers))

# Aggregate
agg_data <- data %>% 
  group_by(participant) %>% 
  summarise(mean_acc = mean(trial_acc),
            sd_acc = sd(trial_acc))

# Plot clean sample
ggplot(data = agg_data,
       mapping = aes(x=1, y = mean_acc)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1)) +
  labs(title = paste("Overall prediction acc"))

```
After removing bad performes, we can look at preformance as a function of prior strength.

```{r}
# Aggregate
agg_data <- data %>% 
  group_by(participant, scn_condition) %>% 
  summarise(mean_acc = mean(trial_acc),
            sd_acc = sd(trial_acc))

# Plot
agg_data$scn_condition <- as.factor(agg_data$scn_condition)
ggplot(data = agg_data,
       mapping = aes(x = scn_condition, y = mean_acc, color = scn_condition)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylim(c(0,1)) +
  ylab("Mean acc") + 
  xlab("Prior strength") +
  labs(title = paste("Prediction acc by prior strength and session")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Weak", "Strong"))
```


## Compute performance at encoding
First I will look at cummulative accuracy.
```{r}

# How many trials in total?
n_trials <- 160 * 4

# How many participants?
n_subs <- length(unique(data$participant))

# Compute cummulative acc by participant and prior strength
data <- data %>% 
  group_by(participant, scn_cat) %>%
  arrange(participant, iteration_index, scn_cat) %>% 
  mutate(cumm_acc = cummean(trial_acc)) %>% 
  mutate(trial_n = rep(c(1:160)))

# Aggregate
agg_data <- data %>% 
  group_by(trial_n, scn_condition) %>% 
  summarise(cumm_av = mean(cumm_acc),
            cumm_sd = sd(cumm_acc))

# Plot
ggplot(data = agg_data,
       mapping = aes(x = trial_n, y = cumm_av, color=factor(scn_condition))) +
  geom_line() +
  facet_wrap(~scn_condition) + 
  ylab("Cummulative acc") + 
  xlab("Trial N") +
  labs(title = paste("Cummulative acc by scene")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Weak", "Strong")) +
  geom_vline(xintercept = 41, linetype = "solid") + geom_vline(xintercept = 81, linetype = "solid") +
  geom_vline(xintercept = 121, linetype = "solid") + geom_vline(xintercept = 160, linetype = "solid") +
     geom_hline(data = agg_data %>% filter(scn_condition==2), aes(yintercept = .9), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==1), aes(yintercept = .7), linetype = "dotted")+
  geom_ribbon(aes(ymin=agg_data$cumm_av- agg_data$cumm_sd, ymax=agg_data$cumm_av+agg_data$cumm_sd), alpha=.2, colour = NA)
 
```


## Last iteration only
Cummulative accuracy.
```{r}
# Compute cummulative acc by participant and prior strength
data_last <- data %>% 
  group_by(participant, scn_condition) %>% 
  filter(iteration_index==4) %>% 
  mutate(cumm_acc = cummean(trial_acc))
data_last$trial_n = rep(c(1:160), n_subs)

# Aggregate
agg_data <- data_last %>% 
  group_by(iteration_index, trial_index, scn_condition) %>% 
  summarise(cumm_av = mean(cumm_acc),
            cumm_sd = sd(cumm_acc))

# Plot
ggplot(data = agg_data,
       mapping = aes(x = trial_index, y = cumm_av, color=factor(scn_condition))) +
  geom_line() +
  facet_wrap(~scn_condition, scales = 'free_y') +  
  ylab("Cummulative acc") + 
  xlab("Trial N") +
  ylim(c(0,1))+
  labs(title = paste("Cummulative acc by scene and group (last iteration only)")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Weak", "Strong")) +
   geom_hline(data = agg_data %>% filter(scn_condition==2), aes(yintercept = .9), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==1), aes(yintercept = .7), linetype = "dotted")+
  geom_ribbon(aes(ymin=agg_data$cumm_av- agg_data$cumm_sd, ymax=agg_data$cumm_av+agg_data$cumm_sd), alpha=.2, colour = NA)
 
```

## Compute performance at encoding (not cumm acc)
I will look at average acc across scene instances on every trial
```{r}

# Get indices by scene
data$trial_ind_scn <- NA
for(c_cat in 1:4){
  
  # Select max cell size
  if(c_cat < 4){
    n_cell <- 160
  }else{
    n_cell <- 160
  }
  
  # Create index
  t <- data %>% 
    group_by(participant) %>% 
    filter(scn_cat == c_cat) %>% 
    mutate(trial_ind_scn = c(1:n_cell))
  
  # Replace index in original data
  data$trial_ind_scn[data$scn_cat == c_cat] <- t$trial_ind_scn
  
}

# Get acc by scn index
t <- data %>% 
    group_by(participant, scn_condition,trial_ind_scn) %>% 
    summarize(av_trial_acc = mean(trial_acc))
  
# Aggregate
agg_data <- t %>% 
  group_by(trial_ind_scn, scn_condition) %>% 
  summarise(mean_acc = mean(av_trial_acc),
            sd_acc = sd(av_trial_acc))

breaks_fun <- function(x) {
  c(1,max(x))
}

 # Plot
ggplot(data = agg_data,
       mapping = aes(x = trial_ind_scn, y = mean_acc, color=factor(scn_condition))) +
  geom_line() +
  facet_wrap(~scn_condition, scales = 'free_x') + 
  ylab("Average acc") + 
  xlab("Trial N") +
  labs(title = paste("Likelihood of choosing the correct object category per trial")) +
   geom_hline(data = agg_data %>% filter(scn_condition==2), aes(yintercept = .9), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==1), aes(yintercept = .7), linetype = "dotted")+
   theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Weak", "Strong")) +
  scale_x_continuous(limits=breaks_fun)+
  geom_ribbon(aes(ymin=agg_data$mean_acc- agg_data$sd_acc, ymax=agg_data$mean_acc + agg_data$sd_acc), alpha=.2, colour = NA)
 
```



And here below I'm printing the IDs of the participants excluded for easier use and communication.

```{r}

"Excluded"
poor_performers

```