---
title: "Analysis of day 2 session (encoding) on PREMUP-pilot. WORK IN PROGRESS"
output: html_document
---

Author: Javier Ortiz-Tudela (Goethe Uni)

```{r setup, include=FALSE}
## Load libraries.
library(ggpubr)
library(rstatix)
library(psycho)
library(gridExtra)
library(dplyr)

## Set directories
if(Sys.info()["sysname"]=="Linux"){
  data_dir <- "/home/javier/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
  out_dir <- "/home/javier/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/" 
}else{
  data_dir <- "/Users/javierortiz/Documents/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
  out_dir <- "/Users/javierortiz/Documents/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-priors/outputs/group_level/share/"
}

## Read-in the data
full_name <- paste(data_dir, "group_task-rec.csv", sep="")

# Since the data is in a CSV file, you can read it with the csvread function.
temp <- read.csv2(full_name, sep=";")

# The data file contains a lot of information that we will not need now.
data <- subset(x = temp,
               select = c("participant", "session", "enc_phase", "mem_phase", "enc_trialN", "enc_acc", "scn_condition", "scn_cat", "PE_level"))

# We'll keep only trials for encoding (old and filler trials)
data <- data %>% 
  filter(data$enc_phase==1)

```

## Compute overall performance
I will compute mean accuracy in both phases of Day2. I will use this information to discard participants below. 

```{r}
# Aggregate
agg_data <- data %>% 
  group_by(participant) %>% 
  summarise(mean_acc = mean(enc_acc),
            sd_acc = sd(enc_acc))
# Plot
ggplot(data = agg_data,
       mapping = aes(x=1, y = mean_acc)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1)) +
  labs(title = paste("Overall categorization acc"))
```

A rather arbitrary threshold of .4 to include _bad luck_ participants which migh have encountered a long train of mismatch trials. I should probably re-consider this.

```{r}
# Poor performers
poor_performers <- agg_data$participant[agg_data$mean_acc < .4]

# Remove poor performers
data <- data %>% 
  filter(!(participant %in% poor_performers))

# Aggregate
agg_data <- data %>% 
  group_by(participant) %>% 
  summarise(mean_acc = mean(enc_acc),
            sd_acc = sd(enc_acc))

# Plot clean sample
ggplot(data = agg_data,
       mapping = aes(x=1, y = mean_acc)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1)) +
  labs(title = paste("Overall prediction acc"))

```
After removing bad performes, we can look at preformance as a function of prior strength.

```{r}
# Aggregate
agg_data <- data %>% 
  group_by(participant, scn_condition) %>% 
  summarise(mean_acc = mean(enc_acc),
            sd_acc = sd(enc_acc))

# Plot
agg_data$scn_condition <- as.factor(agg_data$scn_condition)
ggplot(data = agg_data,
       mapping = aes(x = scn_condition, y = mean_acc, color = scn_condition)) +
  geom_boxplot(outlier.shape = "") +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylim(c(0,1)) +
  ylab("Accuracy") + 
  xlab("Prior strength") +
  labs(title = paste("Categorization accuracy by prior strength and session")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Weak", "Strong"))
```

## Compute performance at encoding
First I will look at cummulative accuracy. It'd be probably best to combine this with the refresh data.
```{r}

# Compute cummulative acc by participant and prior strength
data <- data %>% 
  group_by(participant, scn_condition) %>% 
  mutate(cumm_acc = cummean(enc_acc))

data$trial_n <- NA
data2 <- data %>% 
  group_by(participant, scn_cat) %>%
  filter(scn_condition == 1) %>% 
  mutate(trial_n = c(1:40))
data3 <- data %>% 
  group_by(participant, scn_cat) %>%
  filter(scn_condition == 2) %>% 
  mutate(trial_n = c(1:40))
data <- rbind(data2,data3,data4)
data <- data %>% arrange(participant,day2_trialN)



# Aggregate
agg_data <- data %>% 
  group_by(enc_trialN, scn_condition) %>% 
  summarise(cumm_av = mean(cumm_acc),
            cumm_sd = sd(cumm_acc))
agg_data$cumm_sd[is.na(agg_data$cumm_sd)] <- 0

# Plot
ggplot(data = agg_data,
       mapping = aes(x = enc_trialN, y = cumm_av, color=factor(scn_condition))) +
  geom_line() +
  facet_grid(cols = vars(scn_condition)) + 
  ylab("Cummulative acc") + 
  xlab("Trial N") +
  labs(title = paste("Cummulative acc by scene and group")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Flat", "Strong")) +
  geom_ribbon(aes(ymin=agg_data$cumm_av- agg_data$cumm_sd, ymax=agg_data$cumm_av+agg_data$cumm_sd), alpha=.2, colour = NA)
 
```

And here below I'm printing the IDs of the participants excluded for easier use and communication.

```{r}

"Excluded"
poor_performers

```