---
title: "Analysis of day 1 session (contingency learning) on PREMUP-three."
output: html_document
---

Author: Javier Ortiz-Tudela (Goethe Uni)
Started on: 27.01.20
Last updated on: 05.06.20

```{r setup, include=FALSE}
## Load libraries.
library(ggpubr)
library(rstatix)
library(psycho)
library(gridExtra)
library(dplyr)

## Set directories
if(Sys.info()["sysname"]=="Linux"){
  data_dir <- "/home/javier/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-three/outputs/group_level/share/"
  out_dir <- "/home/javier/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-three/outputs/group_level/share/" 
}else{
  data_dir <- "/Users/javierortiz/Documents/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-three/outputs/group_level/share/"
  out_dir <- "/Users/javierortiz/Documents/pepe/2_Analysis_Folder/PIVOTAL/PREMUP/premup-three/outputs/group_level/share/"
}

## Read-in the data
full_name <- paste(data_dir, "group_task-learning.csv", sep="")

# Since the data is in a CSV file, you can read it with the csvread function.
temp <- read.csv2(full_name, sep=";")

# The data file contains a lot of information that we will not need now.
data <- subset(x = temp,
               select = c("participant", "session", "iteration_index", "trial_index", "trial_acc", "scn_condition", "scn_cat", "PE_level"))

```

## Compute overall performance
I will compute mean accuracy by prior strength in of Day1. I will use this information to discard participants below. 

```{r}
# Aggregate
agg_data <- data %>% 
  group_by(participant, scn_condition) %>% 
  summarise(mean_acc = mean(trial_acc),
            sd_acc = sd(trial_acc))
# Plot
ggplot(data = agg_data,
       mapping = aes(x=scn_condition, y = mean_acc, color = scn_condition)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1)) +
  labs(title = paste("Overall prediction acc"))
```

A rather arbitrary threshold of .4 to include _bad luck_ participants which migh have encountered a long train of mismatch trials. I should probably re-consider this.

```{r}
# Poor performers
poor_performers <- agg_data$participant[agg_data$mean_acc < .5 & agg_data$scn_condition != 1]

# Remove poor performers
data <- data %>% 
  filter(!(participant %in% poor_performers))

# Aggregate
agg_data <- data %>% 
  group_by(participant) %>% 
  summarise(mean_acc = mean(trial_acc),
            sd_acc = sd(trial_acc))

# Plot clean sample
ggplot(data = agg_data,
       mapping = aes(x=1, y = mean_acc)) +
  geom_boxplot() +
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylab("Mean acc") + 
  ylim(c(0,1)) +
  labs(title = paste("Overall prediction acc"))

```
After removing bad performes, we can look at preformance as a function of prior strength.

```{r}
# Aggregate
agg_data <- data %>% 
  group_by(session, participant, scn_condition) %>% 
  summarise(mean_acc = mean(trial_acc),
            sd_acc = sd(trial_acc))

# Plot
agg_data$scn_condition <- as.factor(agg_data$scn_condition)
ggplot(data = agg_data,
       mapping = aes(x = scn_condition, y = mean_acc, color = scn_condition)) +
  geom_boxplot() +
  facet_grid(cols = vars(session)) + 
  geom_jitter(shape=10, position=position_jitter(0.2)) +
  ylim(c(0,1)) +
  ylab("Mean acc") + 
  xlab("Prior strength") +
  labs(title = paste("Mean prediction acc by prior strength and session")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Flat", "Weak", "Strong"))
```


## Compute performance at encoding
First I will look at cummulative accuracy.
```{r}

# How many trials in total?
n_trials <- 240 * 4

# How many participants?
n_subs <- length(unique(data$participant))

# Compute cummulative acc by participant and prior strength
data <- data %>% 
  group_by(participant, scn_cat) %>%
  arrange(participant, iteration_index, scn_cat) %>% 
  mutate(cumm_acc = cummean(trial_acc)) %>% 
  mutate(trial_n = rep(c(1:160))) %>% 
  mutate(tria_n_all = trial_n*iteration_index) 

# Aggregate
agg_data <- data %>% 
  group_by(trial_n, iteration_index, scn_condition) %>% 
  summarise(cumm_av = mean(cumm_acc),
            cumm_sd = sd(cumm_acc))

# Plot
ggplot(data = agg_data,
       mapping = aes(x = trial_n, y = cumm_av, color=factor(scn_condition))) +
  geom_line() +
  facet_grid(cols = vars(scn_condition)) + 
  ylab("Cummulative acc") + 
  xlab("Trial N") +
  labs(title = paste("Cummulative acc by prior condition")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Flat", "Weak", "Strong")) +
  geom_vline(xintercept = 41, linetype = "solid") + geom_vline(xintercept = 81, linetype = "solid") +
  geom_vline(xintercept = 121, linetype = "solid") + geom_vline(xintercept = 161, linetype = "solid") +
  geom_hline(data = agg_data %>% filter(scn_condition==3), aes(yintercept = .9), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==2), aes(yintercept = .7), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==1), aes(yintercept = .5), linetype = "dotted")+
  geom_ribbon(aes(ymin=agg_data$cumm_av- agg_data$cumm_sd, ymax=agg_data$cumm_av+agg_data$cumm_sd), alpha=.2, colour = NA)
 
```


## Last iteration only
Cummulative accuracy.
```{r}
# Aggregate
agg_data <- data %>% 
  group_by(iteration_index, trial_n, scn_condition) %>% 
    filter(iteration_index == 4) %>% 
  summarise(cumm_av = mean(cumm_acc),
            cumm_sd = sd(cumm_acc))

# Plot
ggplot(data = agg_data,
       mapping = aes(x = trial_n, y = cumm_av, color=factor(scn_condition))) +
  geom_line() +
  facet_grid(cols = vars(scn_condition)) + 
  ylab("Cummulative acc") + 
  xlab("Trial N") +
  ylim(c(0,1))+
  labs(title = paste("Cummulative acc by scene and group (last iteration only)")) +
  theme(legend.position = "top") +
  scale_color_discrete(name = "Prior strength", labels= c("Flat", "Weak", "Strong")) +
    geom_hline(data = agg_data %>% filter(scn_condition==3), aes(yintercept = .9), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==2), aes(yintercept = .7), linetype = "dotted")+
  geom_hline(data = agg_data %>% filter(scn_condition==1), aes(yintercept = .5), linetype = "dotted")+
  geom_ribbon(aes(ymin=agg_data$cumm_av- agg_data$cumm_sd, ymax=agg_data$cumm_av+agg_data$cumm_sd), alpha=.2, colour = NA)
 
```

And here below I'm printing the IDs of the participants excluded for easier use and communication.

```{r}

"Excluded"
poor_performers

```