---
title: "PREMUP_bayesian"
output: 
  html_document:
      toc: true
      theme: united
      date: '2022-08-12'
---
Bayesian analyses for the PREMUP studies
```{r setup, include=FALSE}
# load the packages
library("brms")
knitr::opts_chunk$set(echo = TRUE)
```

## Experiment 1
### Model comparison
```{r model comparison, warning=FALSE}
# load the data
load(file="premup_pilot_rec_MLM_bayesian.Rdata")

# results model comparison
mod_comp

# comparing the models and reporting the bayesian  factors
red1_vs_max
BF_red1_vs_max
red2a_vs_red1
BF_red2a_vs_red1
red2b_vs_red1
BF_red2b_vs_red1
red3_vs_red2b
BF_red3_vs_red2b
```

### Analysis winning model
First show some descriptives and diagnostic plots
```{r}
summary(red_model2b)

mcmc_plot(red_model2b, 
          type = "areas", 
          prob = 0.95)

plot(red_model2b)

```
Now analyze the main effects 
```{r}
# interaction
test_inter
BF_test_inter
# test the effect of session
test_session
BF_test_session
# test the effect of PElevel
test_PE
BF_test_PE

# test linear and quadratic interaction with session
hlinearinteraction
hquadraticinteraction

# main trends
hlinear
hquadratic

# now immediate and delayed
hlinear_immediate

red_model2b_immediate

hlinear_delayed

red_model2b_delayed
```

Analyze confidence ratings
```{r}
# compare the winning model (2b) with the same model with the addition of 
# confidence (low vs high)
# (NB: we needed to create a new model - red_model2b_noNA - with some trials
# with NAs on the confidence excluded = 36 in total)

red2b_conf_vs_red2b

# Bayes factor
BF_red2b_conf_vs_red2b

# now we want to test the interaction between confidence and session
red2b_conf_inter_vs_red2b_conf
BF_red2b_conf_inter_vs_red2b_conf

# add the interaction between session and confidence
red_model2b_conf_noPEthreeway_inter

# compare it with a model without that interaction
red2b_conf_sess_by_conf_vs_red2b_conf
BF_red2b_conf_sess_by_conf_vs_red2b_conf

# now add the interaction with PE
red_model2b_twowayPE_inter_vs_red2b_conf

# compare it with a model without that interaction
red_model2b_twowayPE_inter
BF_red_model2b_twowayPE_inter_vs_red2b_conf

# now test the three way interaction
red_model2b_conf_inter
red2b_conf_inter_vs_red_model2b_conf_two_inter
BF_red2b_conf_inter_vs_red_model2b_conf_two_inter

# evidence for quadratic component in the high-confidence items
hquadratic_high

# evidence for the quadratic component in the low-confidence items
hquadratic_low

# remove all the variables
rm(list=ls())
```

## Experiment 2a
### Model comparison
```{r, warning=FALSE}
# load the data
load(file="premup_flat_rec_MLM_bayesian.Rdata")

# results model comparison
mod_comp

# comparing the models and reporting the bayesian  factors
red1_vs_max
BF_red1_vs_max
red2a_vs_red1
BF_red2a_vs_red1
red2b_vs_red1
BF_red2b_vs_red1
red3_vs_red2b
BF_red3_vs_red2b
```

### Analysis winning model
First show some descriptives and diagnostic plots
```{r}
summary(red_model2b)

mcmc_plot(red_model2b, 
          type = "areas", 
          prob = 0.95)

plot(red_model2b)

```
Now analyze the main effects 
```{r}
# interaction
test_inter
BF_test_inter
# test the effect of session
test_session
BF_test_session
# test the effect of PElevel
test_PE
BF_test_PE
# test the NULL effect of PElevel
BF_test_PE01

# test the NULL effect of PElevel on the first half
test_inter_1half
BF_test_inter_1half

test_PE_1half
BF_test_PE_1half

BF_test_PE01_1half
```

Analysis confidence
```{r}
# test the model with confidence vs model without confidence
red2b_conf_vs_red2b
BF_red2b_conf_vs_red2b

# test the interaction with sesison
red2b_conf_sess_by_conf_vs_red2b_conf
BF_red2b_conf_sess_by_conf_vs_red2b_conf

# test the two way interaction with PE
red_model2b_twowayPE_inter_vs_red2b_conf
BF_red_model2b_twowayPE_inter_vs_red2b_conf

# test the three way interaction
red2b_conf_inter_vs_red2b_conf
BF_red2b_conf_inter_vs_red2b_conf

rm(list=ls())

```

## Experiment 2b
### Model comparison
```{r, warning=FALSE}
# load the data
load(file="premup_priors_rec_MLM_bayesian.Rdata")

 # results model comparison
mod_comp

# comparing the models and reporting the bayesian  factors
red1_vs_max
BF_red1_vs_max
red2a_vs_red1
BF_red2a_vs_red1
red2b_vs_red1
BF_red2b_vs_red1
red3_vs_red2b
BF_red3_vs_red2b
```

### Analysis winning model
First show some descriptives and diagnostic plots
```{r}
summary(red_model2b)

# select only some variables to plot
vars<-c("b_Intercept", "b_PE_level.L", "b_PE_level.Q", "b_session_contr", 
        "b_PE_level.L:session_contr", "b_PE_level.Q:session_contr", 
        "sd_participant__Intercept", "sd_participant__session_contr", 
        "cor_participant__Intercept__session_contr")


mcmc_plot(red_model2b, 
          type = "areas", 
          prob = 0.95,
          variable = vars
          )

plot(red_model2b)

```
Now analyze the main effects 
```{r}
# interaction
test_inter
BF_test_inter
# test the effect of session
test_session
BF_test_session
# test the effect of PElevel
test_PE
BF_test_PE

# test the NULL effect of PElevel
BF_test_PE01

# test the NULL effect of PElevel on the first half
test_inter_1half
BF_test_inter_1half

test_PE_1half
BF_test_PE_1half

BF_test_PE01_1half
```

Now analyze the confidence data
```{r}
# test a model with confidence
red2b_conf_vs_red2b
BF_red2b_conf_vs_red2b

# test the interaction with session
red2b_conf_sess_by_conf_vs_red2b_conf
BF_red2b_conf_sess_by_conf_vs_red2b_conf

# test the interaction with PE
red_model2b_twowayPE_inter_vs_red2b_conf
BF_red_model2b_twowayPE_inter_vs_red2b_conf

# check the three-way interaction with PE
red2b_conf_inter_vs_red2b_conf
BF_red2b_conf_inter_vs_red2b_conf

# remove
rm(list=ls())

```

## Experiment 3
### Model comparison
```{r, warning=FALSE}
# load the data
load(file="premup_three_rec_MLM_bayesian.Rdata")

# results model comparison
mod_comp

# comparing the models and reporting the bayesian  factors

# full model vs model without random slopes for PE
red1_vs_max
BF_red1_vs_max

# full model vs model without random intercept for participant
red2a_vs_red1
BF_red2a_vs_red1

```

### Analysis winning model
First show some descriptives and diagnostic plots
```{r}
summary(red_model1)

vars_t<-c("b_Intercept", "b_PE_level.L", "b_PE_level.Q", "b_session_contr", 
        "b_PE_level.L:session_contr", "b_PE_level.Q:session_contr", 
        "sd_participant__Intercept" 
        )


mcmc_plot(red_model1, 
          type = "areas", 
          prob = 0.95, 
          variable = vars_t)

plot(red_model1)

```
Now analyze the main effects 
```{r}
# interaction
test_inter
BF_test_inter

# test the effect of session
test_session
BF_test_session

# test the effect of PElevel
test_PE
BF_test_PE

# test linear and quadratic interaction with session
hlinearinteraction<-hypothesis(red_model1, c("PE_level.L:session_contr=0",
                                              "PE_level.L:session_contr>0", 
                                             "PE_level.L:session_contr<0"))
hlinearinteraction

hquadraticinteraction

 # main trends
hlinear
hquadratic

hlinear_delayed

hlinear_immediate


```

Now confidence
```{r}
# test the addition of confidence
red1_conf_vs_red2b
BF_red1_conf_vs_red2b

# test the interaction with PE
red_model1_twowayPE_inter_vs_red1_conf
BF_red_model1_twowayPE_inter_vs_red1_conf

# test the interaction with session
red_model1_twowaysession_inter_vs_red1_conf
BF_red_model1_twowaysession_inter_vs_red1_conf

# test the triple way interaction
red1_conf_inter_vs_red1_conf
BF_red1_conf_inter_vs_red1_conf
```
